\begin{enumerate}
%	\item Describe how common and vastly used Scrum is.
	\item Describe what Scrum does, that works well in the industry.
	\item Describe what Scrum does, that DOESN'T works well in the industry. - Self-organised chaos. Process improvement on team level (bad retrospectives).
	\item Introduce Lean as solution. (Later: How will Lean deal with the well-functioning timeboxing vs. flow?)
\end{enumerate}

Scrum is currently the most used agile framework. According to the \textit{9th Annual State of Agile™ Survey} \citep{VersionOne}, 56\% of the companies that do agile development use Scrum and at least 16\% more use Scrum combined with something else.

The overall principles of Scrum were first introduced by \citet{Takeuchi1986}, formalised a few years later by \citet{Schwaber} and it has since been refined into what it is today.
They describe Scrum as a lightweight framework for managing complex product development. 

Scrum has become a success because it allows for flexibility as well as predictability.
Especially well-functioning aspects are, but not limited to:
\begin{itemize}
	\item Timeboxing - Using a timebox called “sprint”, Scrum focuses the attention to the next timebox without getting distracted by future tasks. This practice is widely used and liked by the industry, according to XXX.
	\item Planning - Scrum provides multiple planning activities and artefacts for the sprint planning as well as daily task planning. According to XXX Scrum planning activities are widely used with good results.
	\item ...
\end{itemize}

Although Scrum has several good aspects, some can prove to be counter productive in certain contexts.
 
 
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%% TEMP TANKER%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\item Er der altid både ScrumMaster og Project Manager?
	\item Er det muligt at splitte Team Leader rollens opgaver mellem SC og PM. E.g. Process Improvement til SM og tracking til PM.
\end{itemize}







Problems:
\begin{itemize}
	\item Distributed teams.
	\item Using good procedures, but not good practices. E.g. no unit test as standard.
	\item Lack of support tools, e.g. automated tests, one-click deployment.
	\item Too much focus on maintaining velocity.
	\item Scheduling time for exploratory projects.
	\item Handling of unexpected fire fighting e.g. “We didn't set aside 2 days for fixing an issue, but had to do it anyway, now our sprint is running behind, what do we do?”
	\item Understand and Estimation of/in story points.
	\item Bad Product owners. No authority, not reachable, etc.
	\item Impossible to answer client about final release date.
	\item Where do the UX design fit into an iteration?
	\item “Amount of perceived rework as substantially higher since many "architectural concerns" are not discussed immediately because they are not necessary for "the minimum thing that works." It takes experienced designers to keep the amount of rework and speculative features balance under control.”
	\item Wrong use of stand-up meetings. e.g. Product owner runs meeting; management status instead of actual help to team.
	\item Agile/Scrum is isolated to the development team but the rest of the organization continues to function "the old way".
	\item Financial forecasting and budgeting ahead for a full year make being "adaptable" challenging.
	\item Team members not allocated full-time.
	\item When a Project Manager migrates to a Scrum Master role, making the leap from command and control to a facilitating/enabling role.
	\item MINDSET
	\item Legacy code. How can we cope with it (maintain/rewrite/test cover) and how do we make sure new teams do feel responsible for it as well?
	\item Architecture. How do we deal with emergent vs. upfront architecture in Scrum? How do we apply changes to the architecture (consult and involve architect vs. everybody by themselves)? Is there an architect role allowed at all and if so, how to involve him/her?
	\item Defects. How to integrate in the PB or defect backlog? How to plan them? How to deal with an overwhelming count of defects (QA sprints vs. on the fly)
	\item  A scrummaster acting as a teamleader (command - control).
	\item Personalities within a scrum team are not balanced well.
	\item Stand up meetings take too long.
	\item Retrospectives are getting boring
	\item 
\end{itemize}
 
 
 
 
 
 
 
 
The idea of self-organising teams was introduced in XXX due to the problems with the previous approach of XXX.
... many occurrences of self-organising teams turning to self-organising chaos are reported ...
... this problem is, according to XXX, often due to either failed implementation, misunderstood values, or poor/lack of leadership. ...

The aspect of process improvement on the team level are in Scrum managed by the retrospective meetings. These meeting, however, are reported by XXX, XXX, and XXX to often be poorly conducted, unfruitful, and a waste of time. 

... looked at frameworks which values process improvement on the team level ...
... Lean ... Lean may be an option for solving some of the shortcomings of Scrum. ...



Plan 06-10-2015:
\begin{enumerate}
	\item Complete writing introduction.
	\item Find sources for introduction.
	
	\item Read Grounded Theory and SLR research method.
	\item Create slides with comparison of GT vs. SLR.
	
	\item Write report section about research method.
	
	\item Create slides for introduction.
	\item Potentially rewrite/add to report section introduction.
\end{enumerate}
